Choosing Color Palettes for Data Visualization

### 2021-07-02 pkg/colorspace/paper/useR-2021/slides.Rnw
small improvements, first draft ready
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/colorspace@602 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\textbf{Potential problems:}
\begin{itemize}
  \item Power of color often overestimated.
  \item Color vision deficiencies affect $\sim 8$\% of male and $\sim 0.5$\% of female viewers.
  \item Other physical or technical limitations.
\end{itemize}

@@

{\footnotesize
Source: Mara Averick via Twitter
}

@@

\vspace*{-0.5em}
\begin{footnotesize} 
Probability of wind speeds $>$ 39\,mph (63\,km\,h$^{-1}$), 2019-08-30--2019-09-04.
Source: (\href{https://noaa.gov}{noaa.gov})
\end{footnotesize}

@@

{\footnotesize
Source: White House (2019-09-04)}
\end{minipage}
\hfill
\begin{minipage}{0.51\textwidth}
\includegraphics[width=\textwidth]{../EGU2020/images/tweet.png}

{\footnotesize
Source: U.S. president via Twitter (2019-09-05)}
\end{minipage}

@@

@@

\only<1>{\includegraphics[width=\textwidth]{images/almodovar-madre-original.png}}
\only<2>{\includegraphics[width=\textwidth]{images/almodovar-madre-palette.png}}
\only<3>{\includegraphics[width=\textwidth]{images/almodovar-madre-desaturated.png}}
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}

@@

Movie: \emph{Todo sobre mi madre} (\emph{All About My Mother}, 1999)

@@

Picture source: Sony Pictures Classics via MoMA

@@

\only<2->{Palette: Hadley Mendelsohn}
}

@@

\vspace*{-0.5em}
\begin{center}
{\footnotesize
Palette: \only<1>{Todo sobre mi madre}\only<2>{OrRd (ColorBrewer.org, HCL version)}\phantom{Org}}
\end{center}

@@

Movie: \emph{Tacones lejanos} (\emph{High Heels}, 1991)

@@

Picture source: El Deseo S.A. via Twitter

@@

\only<2->{Palette: Bibiana Fernandez}
}

@@

>>>>

\textbf{Potential problems:}
\begin{itemize}
  \item Power of color often overestimated.
  \item Color vision deficiencies ($\sim 8$\% of male and $\sim 0.5$\% of female viewers).
  \item Other physical or technical limitations.
\end{itemize}

@@

{\footnotesize
\textbf{Source:} Mara Averick via Twitter
}

@@

\vspace*{-0.5em}
\begin{footnotesize} 
\textbf{Risk map:} Probability of wind speeds $>$ 39\,mph (63\,km\,h$^{-1}$), 2019-08-30--2019-09-04.

\textbf{Source:} (\href{https://noaa.gov}{noaa.gov})
\end{footnotesize}

@@

{\footnotesize
\textbf{Source:} White House (2019-09-04)}
\end{minipage}
\hfill
\begin{minipage}{0.51\textwidth}
\includegraphics[width=\textwidth]{../EGU2020/images/tweet.png}

{\footnotesize
\textbf{Source:} U.S. president via Twitter (2019-09-05)}
\end{minipage}

@@

\subsection{Colors by designers, painters, and directors?}

@@

\only<1>{\includegraphics[width=\textwidth]{images/almodovar-madre-original.png}}
\only<2>{\includegraphics[width=\textwidth]{images/almodovar-madre-palette.png}}
\only<3>{\includegraphics[width=\textwidth]{images/almodovar-madre-desaturated.png}}
\end{minipage}
\hfill
\begin{minipage}[t]{0.32\textwidth}

@@

\textbf{Movie:} \emph{Todo sobre mi madre} (\emph{All About My Mother}, 1999)

@@

\textbf{Source:} Sony Pictures Classics via MoMA

@@

\only<2->{\textbf{Palette:} Hadley Mendelsohn}
}

@@

\vspace*{-0.5em}
\begin{center}
{\footnotesize
\textbf{Palette:} \only<1>{Todo sobre mi madre}\only<2>{OrRd (ColorBrewer.org, HCL version)}\phantom{Org}}
\end{center}

@@

\textbf{Movie:} \emph{Tacones lejanos} (\emph{High Heels}, 1991)

@@

\textbf{Source:} El Deseo S.A. via Twitter

@@

\only<2->{\textbf{Palette:} Bibiana Fernandez}
}

@@

\subsection{Wrap-up}
